% Resume Claudio Vinegoni  
\documentclass{resume}
\usepackage{color}
\usepackage{graphics}
\usepackage{eurosym}
\usepackage{margins}  
\usepackage{mhchem}
\usepackage[mark]{gitinfo2}
\usepackage[colorlinks=true,bookmarksopen,plainpages=false]{hyperref}
% For creating hyperlinks in cross references
\hypersetup{
  pdftitle={Resume of Claudio Vinegoni},
  pdfsubject={Resume of Claudio Vinegoni},
  pdfauthor={Claudio Vinegoni - Center for Systems Biology - Harvard University/Massachusetts General Hospital},
  pdfkeywords={Resume,Curriculum Vitae},
}
\renewcommand{\categoryfont}{\sc}
\setlength{\oddsidemargin}{1in}
\setlength{\marginparwidth}{1.2in}\addtolength{\marginparwidth}{-\marginparsep}
 \setlength{\evensidemargin}{\oddsidemargin}
 \setlength{\textwidth}{\paperwidth}
 \addtolength{\textwidth}{-2in}
 \addtolength{\textwidth}{-2\oddsidemargin}
 \addtolength{\textwidth}{\marginparwidth}
 \addtolength{\textwidth}{\marginparsep}
\setlength{\topmargin}{-.5in}
\renewcommand{\labelcitem}{$\diamond$}
\renewcommand{\labelitemi}{$\cdot$}
\newcommand{\first}{$1^{\mbox{\scriptsize st}}$\ }
\newcommand{\second}{$2^{\mbox{\scriptsize nd}}$\ }
\newcommand{\third}{$3^{\mbox{\scriptsize rd}}$\ }
\pdfcompresslevel=9


\pdfbookmark[1]{Resume}{resume}
\author{~~~~~~~~Claudio Vinegoni, Ph.D.}
% ------Address --------------------------------------------------------

\address{ Center for System Biology \\
      MGH, Harvard University \\
    \mbox{\small\tt vinegoni@gmail.com - cvinegoni@mgh.harvard.edu}\\
    \mbox{\small\tt \href{https://cvinegoni.github.io}{Webpage}} - 
    \mbox{\small\tt \href{https://scholar.google.com/citations?user=akI55P0AAAAJ&amp;hl=en}{Google Scholar}} - 
    \mbox{\small\tt \href{http://www.researcherid.com/rid/A-9490-2012}{ResearchID}}
- 
    \mbox{\small\tt \href{https://orcid.org/0000-0002-9818-3639"}{OrcID}}
- 
    \mbox{\small\tt \href{https://pubmed.ncbi.nlm.nih.gov/?term=claudio+vinegoni}{PubMed}}
    - 
    \mbox{\small\tt \href{https://www.researchgate.net/profile/Claudio_Vinegoni}{ResearchGate}}
    - 
    \mbox{\small\tt \href{https://www.linkedin.com/in/vinegoni-claudio}{LinkedIn}}
    

    }
{
  185 Cambridge Street\\
     Boston, MA 02114\\
  (857)891.4272  }

\begin{document}
\maketitle

% ------- Nationality ---------------------------------------------------
\pdfbookmark[2]{Citizenship}{nationality}
\begin{category}{Citizenship}
\citemnobullet  Dual Citizenship: {\bf{USA}}, {\bf{Italy}}.
\end{category}


% ------- Education ---------------------------------------------------
\pdfbookmark[2]{Education}{education}
\begin{category}{Education}
\citem{University of Geneva}, Geneva, Switzerland.\\
Ph.D. in Physics, in the group of Prof. N. Gisin (2002).\\
Thesis title: \href{https://cvinegoni.github.io/publications/thesis/Thesis-PHD.pdf}{{\em Nonlinear Effects in Optical
Fibers}}.

\citem{University of Trento}, Trento, Italy. \\
M.Sc. in Physics, October 1996.\\
Thesis title: \href{https://cvinegoni.github.io/publications/thesis/Thesis-MSc.pdf}{{\em Structure and Vibrational
Properties of Electrochromic
Materials}}
\citemnobullet
\citemnobullet

% --------- Present Appointment  ----------------------------------------------------
\pdfbookmark[2]{Present Appointment}{present}
\begin{category}{Present Appointment}
\citembullet Assistant Professor at the
\href{http://csb.mgh.harvard.edu}{{\em Center for Systems
Biology}}  at MGH-Harvard University (Dir.
Prof. R. Weissleder). \citembullet Director of the In-vivo
Microscopy Core at the \href{http://csb.mgh.harvard.edu}{{\em Center for Systems
Biology}} at MGH-Harvard University. \citembullet Head Laboratory
for Biooptics and Molecular Imaging at the \href{https://cmir.mgh.harvard.edu/lbmi}{{\em
Center for Molecular Imaging
Research}} at MGH-Harvard University.
\end{category}


\end{category}

% --------- Previous Appointment  ----------------------------------------------------
\pdfbookmark[2]{Previous Appointments}{previous}
\begin{category}{Previous Appointments}

 \citembullet {\bf
05/2008--12/2010} Instructor of Radiology at the Center for Systems Biology at MGH-Harvard University ({\em prof. R. Weissleder})

 \citembullet {\bf
09/2007--04/2008} Post-Doc researcher at the Center for Systems Biology at MGH-Harvard University ({\em prof. R. Weissleder})

 \citembullet {\bf
09/2005--08/2007} Post-Doc researcher at the Center for Molecular
Imaging Research CMIR at MGH-Harvard University in the Lab for
Biooptics and Molecular Imaging ({\em prof. V. Ntziachristos})

 \citembullet {\bf
07/2003--08/2005} Post-Doc at the Beckman Institute at the
University of Illinois Urbana-Champaign, in the Biophotonics Imaging
Laboratory.

 \citembullet {\bf
05/2002--06/2003} Guest Research Fellow at Chalmers University
(Sweden)- Photonics Laboratory.

 \citembullet
 {\bf 05/2001--09/2001} Guest researcher at EXFO (Quebec, CAN)

\citembullet {\bf 03/1999--01/2002} Research Assistant at the
University of Geneva, CH

\citembullet {\bf 06/1998--03/1999} Research Assistant at the
University of Pittsburgh, PA.

\citembullet {\bf 03/1997--06/1998} Technical Supervisor of the
Ultrafast Spectroscopy Univ. of Trento (Italy).

\citembullet {\bf 10/1996--03/1997} Technical Supervisor in the Raman
Spectroscopy Laboratory Univ. of Trento (Italy).

\end{category}

% --------- Research Activity ----------------------------------------------------

\pdfbookmark[2]{Personal Statement}{research}
\begin{category}{Personal Statement}
\citemnobullet 
 Assistant Professor in Physics at Harvard Medical School and a faculty member of the Center for Systems Biology at Massachusetts General Hospital. 30 years of experience in optical imaging and the development of several novel optical microscopic and macroscopic molecular imaging techniques for biomedical imaging. In particular, my work has been focused on cancer imaging, functional imaging of engineered tissue, neural imaging and cardiovascular imaging. Recent work involves the development of new imaging platforms and imaging processing techniques for motion compensation for {\it in vivo} heart imaging, development of high throughput high-resolution imaging systems for drug-target engagement, {\it in vivo} and {\it in vitro} studies of pharmacodynamics for different drugs, longitudinal microscopy imaging study of insulitis in mice, and the development of novel high content data analysis and visualization tool. The research background in the optical imaging field includes fluorescence, fluorescence polarization and time resolved measurements, multiphoton and confocal microscopy, Raman spectroscopy, Coherent anti-Stokes Raman Scattering (CARS) imaging, optical coherence microscopy and tomography, mesoscopic imaging, optical projection tomography, and fluorescence molecular tomography in diffusive regime for whole mouse imaging.  
My work focuses also on image processing and signal processing in combination with both machine learning and deep learning for image data analysis and segmentation, image data mining, and the design of software tools for microscopy image data collection and visualization. 


\end{category}
%
% --------- Scientific Contributions ----------------------------------------------------
%
\pdfbookmark[2]{Scientific Contributions}{scientific}
\begin{category}{Scientific Contributions}
\citemnobullet 
Author and coauthor of \href{https://cvinegoni.github.io/diffpubs}{187 scientific contributions}.
Among them, \href{https://cvinegoni.github.io/books/}{3 Invited Review
Chapters}, \href{https://cvinegoni.github.io/patents/}{1 Patent},  \href{https://cvinegoni.github.io/papers/}{114
articles},
 published in peer-reviewed international scientific
journals, \href{https://cvinegoni.github.io/proceedings/\#conferences}{35 oral
presentations}
and poster sessions at international conferences, and
\href{https://cvinegoni.github.io/proceedings/\#proceedings-papers}{34
proceedings}.
\end{category}
%
% --------- Committee Services and Activities ----------------------------------------------------
%
\pdfbookmark[2]{Committee Services and Activities}{committee}
\begin{category}{Committee Services and Activities}
\citembullet 
Editorial Board Member {\it "Discovery Imaging"} Springer Nature.
\citembullet 
Editorial Board {\it "Scientific Reports"} in the category Electronics, Photonics and Device Physics
\citembullet 
Associate Editor {\it "Frontiers in Physics"} in the category Medical Physics and Imaging

\citembullet 
Reviewer for the following journals: {\it Advanced Science, Applied Physics Letters Photonics, Biomedical Optics Express, Biotechnology Journal, Circulation: Cardiovascular Imaging, ACS Chemical and Biomedical Imaging, Cytometry, eLife, F1000research, Frontiers in Physics, Frontiers in Immunology, IEEE Access, IEEE Advances, IEEE Transactions on Information Technology in BioMedicine,  IEEE Transaction on Biomedical Engineering, IEEE Transactions of Instrument and Measurements, IEEE Transactions on Med. Imaging,  IEEE Journal of Biomedical and Health Informatics, Int. J. of Biochemistry, Int. J. of Biomedical Imaging, JACC: Cardiovascular Imaging, Journal of Biophotonics, J. Lightwave Technology, Journal of Mathematical Imaging and Vision, Journal of Microscopy, Journal of Molecular Imaging, Journal Nuclear Medicine, JOVE,  Methods and Applications in Fluorescence, Micromachines, Molecular Imaging, Molecular Imaging and Biology, Nature Communications, Nature Methods, Nature Protocols, Optica, Optics Communications, Optics Express, Optics Letters, Photoacoustics, Photonics and Technology Letters, PhotoniX, Physical Review A, Physical Review E, PlosOne, Review of Scientific Instruments, Scientific Reports, SLAS Discovery.}
\citembullet 
Chair of the "Molecular Infrared and other novel imaging modalities" session at {\it IEEE Engineering Medicine and Biology, Boston USA (2011). }
\citembullet 
Technical Program Committee of the {\it IEEE Biomedical and Health Informatics}, Hong Kong (2012).
\citembullet 
Associate Editor, Biomedical Imaging and Image Processing, {\it IEEE Engineering Medicine and Biology} (2012-2025).
\end{category}

\pdfbookmark[2]{Webpage}{webpage}
\begin{category}{Webpage}
 \citemnobullet 
A copy of this curriculum vitae, a short
resume, and a complete dowloadable bibliography with all the
published articles and conference contributions, can be found on my Webpage at:
\newline
    \mbox{\small\tt \url{https://cvinegoni.github.io}}
\end{category}

\pdfbookmark[2]{Last Updated}{updated}
\begin{category}{Last Updated}
\citemnobullet 
\today{}
\end{category}
%\cite{2002-PTL}

%\printbibliography %Prints bibliography

\end{document}
