\documentclass{resume}
%\documentclass[a4paper,12pt,draft]{report}
\usepackage{color}
\usepackage{graphics}
\usepackage{margins}
\usepackage{eurosym}

\usepackage[colorlinks=true,bookmarksopen]{hyperref}  %bookmarksopenlevel=1,bookmarksopen
\usepackage{palatino}
% For creating hyperlinks in cross references
\hypersetup{
  pdftitle={Selected Publications of Claudio Vinegoni},
  pdfsubject={Selected Publications of Claudio Vinegoni},
  pdfauthor={Claudio Vinegoni - Center for Systems Biology - Harvard University/Massachusetts General Hospital},
  pdfkeywords={Resume,Curriculum Vitae},
}


\renewcommand{\categoryfont}{\sc}
\setlength{\oddsidemargin}{0.0in}
%\setlength{\oddsidemargin}{1in}

\setlength{\marginparwidth}{1.2in}\addtolength{\marginparwidth}{-\marginparsep}
 \setlength{\evensidemargin}{\oddsidemargin}
 \setlength{\textwidth}{\paperwidth}
 \addtolength{\textwidth}{-3in}
 \addtolength{\textwidth}{-2\oddsidemargin}
 \addtolength{\textwidth}{\marginparwidth}
 \addtolength{\textwidth}{\marginparsep}
\setlength{\topmargin}{-0.5in}
\renewcommand{\labelcitem}{$\diamond$}
\renewcommand{\labelitemi}{$\cdot$}
\newcommand{\first}{$1^{\mbox{\scriptsize st}}$\ }
\newcommand{\second}{$2^{\mbox{\scriptsize nd}}$\ }
\newcommand{\third}{$3^{\mbox{\scriptsize rd}}$\ }
\definecolor{Dark}{gray}{.20}


\newcommand{\titresection}[1]
{
  \vspace{0em}
%  \vfill
  \definecolor{gris_clair}{rgb}{0.90, 0.90, 0.90}
  \colorbox{gris_clair}{\makebox[\textwidth][l]{\rule[-0.1em]{0em}{0.5em}\large{\textsc{#1}}}} \\
  %\vspace{0.5em}
}
%\titresection{NAME:}


\newcommand{\tabspace}{~~~}
\newcommand{\indenta}{\lindent{0.3}}
\newcommand{\indentaa}{\lindent{1.3}}



\pagenumbering{gobble}



\begin{document}

\newpage



\tabspace\\
{$^\dag$} \tabspace{equal contribution}\\
{$^*$} \tabspace{corresponding author}\\




\pdfbookmark[1]{Selected Recent Publications}{articles}
\begin{category}{~~}
%\citemnobullet
%\citemnobullet
%\hypertarget{articlesa} {\textbf{\large PUBLICATIONS: ARTICLES}}
\hypertarget{articlesa}{\citemnobullet \titresection{\textbf{\large
SELECTED RECENT PUBLICATIONS}}}

\begin{enumerate}



\item \href{https://tinyurl.com/43npyhfm}{Fluorescence microscopy tensor imaging representations for large scale dataset analysis.}\\
{\bf C. Vinegoni$^*${$^\dag$}}, P. Fumene Feruglio{$^\dag$}, I. G. Courties, S. Schmidt, M. Hulsmans, S. Lee, R. Wang, D. Sosnovik, M. Nahrendorf, R. Weissleder  \\
``Scientific Reports''  Vol. 100 (2020) pp. 5632. \\DOI:10.1038/s41598-020-62233-2. PMID: XX.

\item \href{https://tinyurl.com/k89jzpkf}{CytoPAN—Portable cellular analyses for rapid point-of-care cancer diagnosis .}\\
J. Min, L.K. Chin, J. Oh, C. Landeros, {\bf C. Vinegoni}, J. Lee, S.J. Lee, J.Y. Park, A.Q. Liu, C.M. Castro, H. Lee, H. Im,  R. Weissleder$^*$  \\
``Science Translational Medicine''  Vol. 12: (2020) eaaz9746. \\DOI:DOI:10.1126/scitranslmed.aaz9746. PMID: XX. PMCID: xxx


\item 
\href{https://tinyurl.com/ec59tkbt}{High dynamic range fluorescence imaging.}\\
{\bf C. Vinegoni$^*$}, P. Fumene Feruglio, R. Weissleder\\
``IEEE Journal of Selected Topics in Quantum Electronics, Special Issue on Biophotonics''  Vol. 25 (2019)
 pp. 1-13. \\DOI:110.1109/JSTQE.2018.2881608. PMID: 31598059.
 
\item \href{https://tinyurl.com/24h9yds6}{Fluorescence anisotropy imaging in drug discovery.}\\
 {\bf C. Vinegoni$^*$}, P. Fumene Feruglio, I. Gryczynski, R. Mazitschek, and R. Weissleder\\
``Advanced Drug Delivery Review''  Vol. 151-152 (2019) pp.262-288. \\DOI:10.1016/j.addr.2018.01.019. PMID: 29410158 . PMCID: PMC6072632.
\item 
\href{https://tinyurl.com/24c32k4p}{The anti-tumor diterpene oridonin is a direct inhibitor of Nucleolin in cancer cells.}\\
 M. Vasaturo, R. Cotugno, L. Fiengo, {\bf C. Vinegoni}, {F. Dal Piaz$^*$}, N. De Tommasi \\
``Scientific Reports''  Vol. 8 art.$\#$ 16735 (2018)
 pp. 1209-1219. \\DOI:10.1038/s41598-018-35088-x. PMID: 30425290.


\item
\href{https://tinyurl.com/xwey3azh}{Imaging the Vascular Bone Marrow Niche During Inflammatory Stress.}\\
K. Vandoorne, D. Rohde, H.Y. Kim, G. Courties, G.R. Wojtkiewicz, L. Honold, F.F. Hoyer, V. Frodermann, R. Nayar, F.E. Herisson FE, Y. Jung, P. Désogère, {\bf C. Vinegoni}, P. Caravan, R. Weissleder, D.E. Sosnovik, C.P. Lin, F.K. Swirski, M.P. Nahrendorf$^*$\\
``Circulation Research''  Vol. 123 (2018) pp. 415-427. \\DOI:10.1016/j.addr.2018.01.019. PMID: 29980569. PMCID: PMC6202141
 
\item
\href{https://tinyurl.com/kkk8uns}{Direct vascular channels connect skull bone marrow and the brain surface enabling myeloid cell migration.}\\
 F. Herisson, V. Frodermann, G. Courties, D. Rohde, Y. Sun, K. Vandoorne, G.R. Wojtkiewicz, G. Santos Masson, {\bf C. Vinegoni}, J. Kim, D. Kim, R. Weissleder, F.K. Swirski, M.A. Moskowitz, M. Nahrendorf$^*$\\
``Nature Neuroscience''  Vol. 21 (2018)
 pp. 1209-1219. \\DOI:10.1038/s41593-018-0213-2. PMID: 30150661.


\item
\href{https://tinyurl.com/274jupz9}{Cardiac macrophages promote diastolic dysfunction.}\\
M. Hulsmans, H.B. Sager, J.D. Roh, V. Valero-Munoz, N.E. Houstis, Y. Iwamoto, Y. Sun, R.M. Wilson, G. Wojtkiewicz, B. Tricot, M.T. Osborne, J. Hung, {\bf C. Vinegoni}, K. Naxerova, D.E. Sosnovik, M.R. Zile, A.D. Bradshaw, R. Liao, A. Tawakol, R. Weissleder, A. Rosenzweig, F.K. Swirski, F. Sam, { M. Nahrendorf$^*$}\\
``JEM Journal of Experimental Medicine''  Vol. 512 (2018) pp. 423-440. \\DOI:10.1084/jem.20171274. PMID: 29339450 .


\item
\href{https://tinyurl.com/te7uwuyv}{Measurement of drug-target engagement in live cells by two-photon fluorescence anisotropy imaging.}\\
{\bf C. Vinegoni$^*$}, P. Fumene Feruglio, C. Brand, S. Lee, A.E. Nibbs, S. Stapleton, S. Shah, I. Gryczynski, R. Mazitschek, and R. Weissleder \\
``Nature Protocols''  Vol. 12 (2017) pp. 1472-1497. \\DOI:10.1038/nprot.2017.043. PMID: 28686582. PMCID: PMC5789416 

\item
\href{https://tinyurl.com/8exdu6w}{Macrophages facilitate electrical conduction in the heart.}\\
M. Hulsmans, S. Clauss, L. Xiao, A.D. Aguirre, K.R. King, A. Hanley, W.J. Hucker, E.M. Wülfers, G. Seemann, G. Courties, Y. Iwamoto, Y. Sun, A.J. Savol, H.B. Sager, K.J. Lavine, G.A. Fishbein, D.E. Capen, N. Da Silva, L. Miquerol, H. Wakimoto, C.E. Seidman, J.G. Seidman, R.I. Sadreyev, K. Naxerova, R.N. Mitchell, D. Brown, P. Libby, R. Weissleder, F.K. Swirski, P. Kohl, {\bf C. Vinegoni}, D.J. Milan, P.T. Ellinor, M. Nahrendorf$^*$ \\
``Cell''  Vol. 169 (2017) pp. 510-222. \\DOI:10.1016/j.cell.2017.03.050. PMID: 28431249. PMCID: PMC5474950.

\item
\href{https://tinyurl.com/2py4t3nn}{Quantitating drug-target engagement in single cells in vitro and in vivo.}\\
J.M. Dubach, E. Kim, K. Yang, M. Cuccarese, R.J. Giedt, L.G. Meimetis, {\bf C. Vinegoni$^*$}, R. Weissleder$^*$.\\
 ``Nature Chemical Biology'', Vol. 13 (2017) pp. 168--173. \\DOI:10.1038/nchembio.2248. PMID: 27918558.

\item
\href{https://tinyurl.com/3hj8uvwe}{Computational imaging reveals mitochondrial morphology as a biomarker of cancer phenotype and drug response.}\\
R.J. Giedt, P. Fumene Feruglio, D. Pathania, K.S. Yang, A. Kilcoyne, {\bf C. Vinegoni}, T.J. Mitchison, R. Weissleder.\\
 ``Scientific Reports'', Vol. 6 (2016) art.$\#$ 32985. \\DOI: 10.1038/srep32985. PMID: 27609668. PMCID: PMC5017129.

\item
\href{https://tinyurl.com/y4hpumay}{RNAi targeting multiple cell adhesion molecules reduces immune cell recruitment and vascular inflammation after myocardial infarction.}\\
H.B. Sager, P. Dutta, J.E. Dahlman, M. Hulsmans, G. Courties, Y. Sun, T. Heidt, {\bf C. Vinegoni}, A. Borodovsky, K. Fitzgerald, G.R. Wojtkiewicz, Y. Iwamoto, B. Tricot, O.F. Khan, K.J. Kauffman, Y. Xing, T.E. Shaw, P. Libby, R. Langer, R. Weissleder, F.K. Swirski, D.G. Anderson, and M. Nahrendorf.\\
 ``Science Translational Medicine'', Vol. 8 (2016) art.$\#$ 342ra80. \\DOI:
10.1126/SCITRANSLMED.aaf1435 . PMID: 27280687. PMCID: PMC5125383.

\item
\href{https://tinyurl.com/jrvjrusj}{Real-time high dynamic range laser scanning microscopy.}\\
{\bf C. Vinegoni$^*${$^\dag$}}, C. Leon Swisher$^\dag$, P. Fumene Feruglio$^\dag$, R.J. Giedt, D.L. Rousso, S. Stapleton, R. Weissleder.\\
 ``Nature Communications'', Vol. 7 (2016) art.$\#$ 11077. \\DOI:
10.1038/ncomms11077. PMID: 27032979. PMCID: PMC4821995.

\item
\href{https://tinyurl.com/yx8ye7m3}{Tyrosine kinase-mediated axial motility of basal cells revealed by intravital imaging.}\\
J. Roy, B. Kim, E. Hill, P. Visconti, D. Krapf, {\bf C. Vinegoni}, R. Weissleder, D. Brown, S. Breton.\\
 ``Nature Communications'', Vol. 7 (2016) art.$\#$ 10666 \\DOI:
10.1038/ncomms10666. PMID: 26868824. PMCID: PMC4754344.

\item
\href{https://tinyurl.com/y7uz4zbp}{Two-photon fluorescence anisotropy microscopy for imaging and direct measurement of intracellular drug target engagement.}\\
{\bf C. Vinegoni$^*$}, M. Dubach, P. Fumene Feruglio, and R. Weissleder.\\
 ``Selected Topics in Quantum Electronics, IEEE'', Vol. 22 (2016) art.$\#$ 6801607. \\DOI:
10.1109/JSTQE.2015.2501384. PMID: 27440991. PMCID: PMC4946648.


\item
\href{https://tinyurl.com/3njutdnt}{Imaging the beating heart in the mouse using intravital microscopy techniques.}\\
{\bf C. Vinegoni$^*$}, A.D. Aguirre, S. Lee, R. Weissleder.\\
 ``Nature Protocol'', Vol. 10 (2015) pp. 1802--19. \\DOI: 10.1038/nprot.2015.119. PMID: 26492138. 

\item
\href{https://tinyurl.com/nufk6x9h}{Rapid, high efficiency isolation of pancreatic beta-cells.}\\
S.M. Clardy, J.F. Mohan, {\bf C. Vinegoni}, E.J. Keliher, Y. Iwamoto, C. Benoist, D. Mathis, R. Weissleder.\\
 ``Scientific Reports'', Vol. 5 (2015) art.$\#$ 13681. \\DOI: 10.1038/srep13681. PMID: 26330153. PMCID: PMC4557033

\item
\href{https://tinyurl.com/27kj77xh}{Advances in measuring single-cell pharmacology in vivo.}\\
 {\bf C. Vinegoni$^*$}, J.M. Dubach, G.M. Thurber, M.A. Miller, R. Mazitschek, R. Weissleder.\\
 ``Drug Discovery Today'', Vol. 20 (2015) pp. 1087--92. \\DOI: 10.1016/j.drudis.2015.05.011. PMID: 26024776. PMCID: PMC4567932

\item
\href{https://tinyurl.com/9mw5etwc}{New techniques for motion-artifact-free in vivo cardiac microscopy.}\\
 {\bf C. Vinegoni$^*${$^\dag$}}, S. Lee{$^\dag$}, A.D. Aguirre, R. Weissleder. \\
 ``Frontiers in Physiology'', Vol. 6 (2015) art.$\#$ 147. \\DOI: 10.3389/fphys.2015.00147. PMID: 26029116. PMCID: PMC4428079

\item
\href{https://tinyurl.com/3kzjb3a6}{Myocardial Infarction Activates CCR2(+) Hematopoietic Stem and Progenitor Cells.}\\
P. Dutta, H.B. Sager, K.R. Stengel, K. Naxerova, G. Courties, B. Saiez, L. Bilberstein, T. Heidt, M. Sebas, Y. Sun, G. Wojtkiewicz, P.F. Feruglio, K. King, J.N. Baker, A.M. van der Laan, A. Borodovsky, K. Fitzgerald, M. Hulsmans, F. Hoyer, Y. Iwamoto, {\bf C. Vinegoni}, D. Brown, M. Di Carli, P. Libby, S.W. Hiebert, D.T. Scadden, F.K. Swirski, R. Weissleder, M. Nahrendorf.\\
 ``Cell Stem Cell'', Vol. 16 (2015) pp. 477--87. \\DOI: 10.1016/j.stem.2015.04.008. PMID: 25957903. PMCID: PMC4426344

\item
\href{https://tinyurl.com/vf68d5zj}{ Intravital imaging of cardiac function at the single-cell level.}\\
A.D. Aguirre,  {\bf C. Vinegoni$^*$}, M. Sebas, R. Weissleder$^*$. \\
 ``PNAS'', Vol. 111 (2014) pp. 11257--62. \\DOI: 10.1073/pnas.1401316111. PMID: 25053815. PMCID: PMC4128110

\item
\href{https://tinyurl.com/2z2fdum5}{Chronic variable stress activates hematopoietic stem cells.}\\
T. Heidt, H.B. Sager, G. Courties, P. Dutta, Y. Iwamoto, A. Zaltsman, C. von zur Muhlen, C. Bode, G.L. Fricchione, J. Denninger, C.P. Lin,  {\bf C. Vinegoni}, P. Libby, F.K. Swirski, R. Weissleder, R. Weissleder, M. Nahrendorf. \\
 ``Nature Medicine'', Vol. 20 (2014) pp. 754--8. \\DOI: 10.1038/nm.3589. PMID: 24952646. PMCID: PMC4087061 

\item
\href{https://tinyurl.com/j2288nha}{In vivo imaging of specific drug-target binding at subcellular resolution.}\\
M. Dubach{$^\dag$}, {\bf C. Vinegoni$^*${$^\dag$}},  R. Mazitschek, P. Fumene Feruglio, L.A. Cameron, R. Weissleder. \\
 ``Nature Communications'', Vol. 5 (2014) art.$\#$ 3946. \\DOI: 10.1038/ncomms4946. PMID: 24867710. PMCID: PMC4362617 

\item
\href{https://tinyurl.com/yysfh9mj}{Automated motion artifact removal for intravital microscopy, without a priori information.}\\
 S. Lee{$^\dag$}, {\bf C. Vinegoni$^*${$^\dag$}},  M. Sebas, R. Weissleder. \\
 ``Scientific Reports'', Vol. 4 (2014) art.$\#$ 4507. \\DOI: 10.1038/srep04507. PMID: 24676021. PMCID: PMC3968488 

\item
\href{https://tinyurl.com/347m34a9}{Advanced Motion Compensation Methods for Intravital Optical Microscopy.}\\
 {\bf C. Vinegoni$^*${$^\dag$}},  S. Lee{$^\dag$}, P.F. Feruglio, R. Weissleder. \\
 ``Selected Topics in Quantum Electronics, IEEE'', Vol. 20 (2014) art.$\#$ 6800709. \\DOI: 10.1109/JSTQE.2013.2279314. PMID: 24273405. PMCID: PMC3832946 

\item
\href{https://tinyurl.com/k4wuk5zp}{Implantable microenvironments to attract hematopoietic stem/cancer cells.}\\
J. Lee, M. Li, J. Milwid, J. Dunham, {\bf C. Vinegoni}, R. Gorbatov, Y. Iwamoto, F. Wang, K. Shen, K. Hatfield, M. Enger, S. Shafiee, E. McCormack, B.L. Ebert, R. Weissleder, M.L. Yarmush, and B. Parekkadan.\\
 ``PNAS'', Vol. 109 (2012) pp. 19638--43. \\DOI: 10.1073/pnas.1208384109. PMID: 24086796. PMCID: PMC3786172 

\item
\href{https://tinyurl.com/e98jaep}{Real-time in vivo imaging of the beating mouse heart at microscopic resolution.}\\
S. Lee{$^\dag$}, {\bf C. Vinegoni$^*${$^\dag$}}, P. Fumene Feruglio, L. Fexon, R. Gorbatov, M. Pivoravov, A. Sbarbati, M. Nahrendorf, R. Weissleder.\\
 ``Nature Communications'', Vol. 3 (2012) art.$\#$ 1054. \\DOI: 10.1038/ncomms2060. PMID: 22968700. PMCID: PMC3622400 

\item
\href{https://tinyurl.com/cwd5vabf}{Bioorthogonal Imaging of Aurora Kinase A in Live Cells.}\\
K.S. Yang, G. Budin, T. Reiner, {\bf C. Vinegoni}, and R. Weissleder.\\
 ``Angewandte Chemie'', Vol. 51 (2012) pp. 6598--6603. \\DOI: 10.1002/anie.201200994. PMID: 22644700. PMCID: PMC3523717 

\item
\href{https://tinyurl.com/4cyrytuk}{Deep Tissue Optical and Optoacoustic Molecular Imaging Technologies for Pre-Clinical Research and Drug Discovery.}.\\
 D. Razansky, N. Deliolanis, {\bf C. Vinegoni}, and V. Ntziachristos.\\
 ``Current Pharmaceutical Biotechnology'', Vol. 13 (2012) pp. 504--22. \\DOI: 10.2174/138920112799436258. PMID: 22216767 

\item
\href{https://tinyurl.com/5fm8vmw9}{Myocardial infarction accelerates atherosclerosis.}\\
Dutta P, Courties G, Wei Y, Leuschner F, Gorbatov R, Robbins CS, Iwamoto Y, Thompson B, Carlson AL, Heidt T, Majmudar MD, Lasitschka F, Etzrodt M, Waterman P, Waring MT, Chicoine AT, van der Laan AN, Niessen HWM, Piek JJ, Rubin BB, Butany J, Stone JR, Katus HA, Murphy SA, Morrow DA, Sabatine MS, Vinegoni C, Moskowitz MA, Pittet MJ, Libby P, Lin CP, Swirski FK, Weissleder R, Nahrendorf MW.W. Lee, B. Marinelli, A.M. van der Laan, B.F. Sena, R. Gorbatov, F. Leuschner, P. Dutta, Y. Iwamoto, T. Ueno, M.P. Begieneman, H.W. Niessen, J.J. Piek, {\bf C. Vinegoni}, M.J. Pittet, F.K. Swirski, A. Tawakol, M. Di Carli, R. Weissleder, M. Nahrendorf.\\
 ``Nature'', Vol. 487 (2012) pp. 325--29. \\DOI: 10.1038/nature11260. PMID: 22763456. PMCID: PMC3401326 

\item
\href{https://tinyurl.com/2495rfpz}{Accurate measurement of pancreatic islet beta-cell mass using a second-generation fluorescent exendin-4 analog.}\\
T. Reiner, G. Thurber, J. Gaglia, {\bf C. Vinegoni}, C.W. Liew, R.
Upadhyay, R.H. Kohler, L. Li, R.N. Kulkarni, C. Benoist, D. Mathis,
R. Weissleder\\
 ``PNAS'', Vol. 108 (2011) pp. 12815--20. \\DOI: 10.1073/pnas.1109859108. PMID: 21768367. PMCID: PMC3150928 

\item
\href{https://tinyurl.com/k274eyac}{Indocyanine Green Enables Near-Infrared Fluorescence Imaging of Lipid-Rich, Inflamed Atherosclerotic Plaques.}\\
{\bf C. Vinegoni}, I. Botnaru, E. Aikawa,
M.A. Calfon, Y. Iwamoto, E.J. Folco, V. Ntziachristos, R. Weissleder, P. Libby, F. Jaffer\\
 ``Science Translational Medicine'', Vol. 3 (2011) art.$\#$ 84ra45. \\DOI: 10.1126/scitranslmed.3001577. PMID: 21613624. PMCID: PMC3112179

\item
\href{https://tinyurl.com/ytvfcw7y}{ Hybrid PET-optical imaging using targeted probes.}\\
M. Nahrendorf, E. Keliher, B. Marinelli, P. Waterman, P. Fumene Feruglio, L. Fexon, M. Pivovarov, F.K. Swirski, M. Pittet,
{\bf C. Vinegoni}, and R. Weissleder.  \\
 ``PNAS'', Vol. 107 (2010) pp. 7910--15. \\DOI: 10.1073/pnas.0915163107. PMID: 20385821 PMCID: PMC2867879

\item
\href{https://tinyurl.com/wj6bzyy}{Unprecedented in vivo views at the mesoscopic scale.}\\
D. Razansky, {\bf C. Vinegoni}, and V. Ntziachristos \\
 ``BioOptics World'', Vol. 2 (2009) pp. 22--25. 

\item
\href{https://tinyurl.com/238k7whp}{Multispectral opto-acoustic tomography of deep-seated fluorescent proteins in vivo.}\\
D. Razansky, M. Distel, {\bf C. Vinegoni}, R. Ma, N. Perrimon, R.W. Koster, V. Ntziachristos. \\
 ``Nature Photonics'', Vol. 3 (2009) pp. 412--17. \\DOI: 10.1038/NPHOTON.2009.98

\item
\href{https://tinyurl.com/5uyp8uhd}{In vivo imaging of Drosophila melanogaster pupae with mesoscopic fluorescence tomography.}\\
{\bf C. Vinegoni$^*${$^\dag$}}, C. Pitsouli$^\dag$, D. Razansky$^\dag$, N. Perrimon, V. Ntziachristos\\
 ``Nature Methods'', Vol. 5, (2008) pp. 45--8. \\DOI: 10.1038/NMETH1149. PMID: 18066071

\item
\href{https://tinyurl.com/y7zaft8r}{Nonlinear Interferometric Vibrational Imaging: Efficient detection of Coherent Anti-Stokes Raman Scattering.}
 \\
D. Marks, {\bf C. Vinegoni}, J. Bredfeldt, and  S.A. Boppart\\
``OPN Special Issue'', ``Optics in 2005'', Vol. 16, (2005) pp. 23. \\DOI: 10.1364/OPN.16.12.000023











\end{enumerate}
\end{category}




%------------------------URL-----------------------
\begin{category}{~~}
%\citemnobullet
%\citemnobullet \hypertarget{booksa}{\textbf{\large PUBLICATIONS:
%BOOKS}}
\hypertarget{lastupdated}{\citemnobullet \titresection{\textbf{\large
LAST UPDATED}}}

\pdfbookmark[2]{Last Updated}{updated}
 \indenta \today{}



\end{category}


\end{document}